Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-27 robdml.tex
tex

As shown in the last three columns of \cref{tab:desth}, almost all combinations
lead to model collapse as long as $H_\mathsf{D}$ is calculated from a Softhard,
Distance, or Hardest triplet.
%
Due to the small $E[H_\mathsf{D}-H_\mathsf{S}]$ in the combination of Distance
and Hardest triplets, the adversarial examples will be weak and the model does
collapse, but the robustness gain is negligible.
%
Although $E[H]$ of Softhard is less than that of Distance or Hardest,
some hard adversarial examples are still created due to its large
$\text{Var}[H]$, which still result in a slow collapse.

@@

For cases in lower triangular of \cref{tab:desth}, $E[H_\mathsf{S}] \geqslant E[H_\mathsf{D}]$,
which means most tirplet will not be turned into adversarial according to
\cref{eq:hm}.
%
In such cases, the model will not be able to effectively learn from a strong
adversary, and hence will behave as if no defense is equipped.
%
As an exception, HM from softhard to semihard can also lead to relatively high
adversarial robustness.
%
Due to the high variance of hardness of softhard sampling strategy, the
hardness of a notable portion of triplets will be less than that of semihard,
and hence HM will create some adversarial examples for training.
%
In other words, HM in this case can be interpreted as mixing some unperturbed
softhard triplets and some semihard adversarial triplets.

>>>>

As shown in the last three columns of \cref{tab:desth}, almost all combinations
lead to model collapse as long as $H_\mathsf{D}$ is calculated from a Softhard,
Distance, or Hardest triplet.
%
Due to the small $E[H_\mathsf{D}-H_\mathsf{S}]$ in the combination of Distance
and Hardest triplets, the adversarial examples will be weak and the model does
collapse, but the robustness gain is negligible.
%
Although $E[H]$ of Softhard is less than that of Distance or Hardest,
some hard adversarial examples are still created due to its large
$\text{Var}[H]$, which still result in a slow collapse.
\todo{merge this para into upper triangular and lower triangular}

@@

For cases in lower triangular of \cref{tab:desth}, where $E[H_\mathsf{S}]
\geqslant E[H_\mathsf{D}]$, a large portion of given triplets will be
unchanged according to \cref{eq:hm}, and hence lead to weak robustness.
%
As an exception, $\text{HM}[\mathcal{S},\mathcal{M}]$ is still effective in
improving adversarial robustness, where a notable number of adversarial
examples are created due the high $\text{Var}[H]$ of Softhard.
%
%
%
In other words, HM in this case can be interpreted as mixing some unperturbed
softhard triplets and some semihard adversarial triplets.
